---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Qiran Wang (12626372)"
date: "`r Sys.Date()`"
output: distill::distill_article
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `2024-exeRcise-sheet-3`. If you forgot how to do this, you can
    follow this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*)
    
  Strengths:
  1. Very hard to lose files with git
  2. Really fast
  
  Weaknesses:
  1. History takes up file space (only little)
  2. Struggles with large files
    
e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (3.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2023` and
`2022`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.

```{r}
vornamen_2022 <- read.csv("data/open_data_portal_2022.csv")
vornamen_2023 <- read.csv("data/vornamen-muenchen-2023.csv")

str(vornamen_2022)
str(vornamen_2023)
# The type of the count variable ("Anzahl") is character.
# In the data of 2022, there are NA values; in the data of 2023, there are non-numeric values "4 oder weniger".

# Fix the problem
# Replacing NA values with 0
vornamen_2022$Anzahl[is.na(vornamen_2022$Anzahl)] <- 0
# Replace non-numeric values "4 oder weniger" with 4 and convert to numeric
vornamen_2023$Anzahl <- as.numeric(ifelse(vornamen_2023$Anzahl == "4 oder weniger", 4, vornamen_2023$Anzahl))
```

Repercussions:
While replacing non-numeric values with an approximation and handling NA values with 0 helps in ensuring the data's integrity, it may lead to inaccurate counts. For instance, counts of "4 oder weniger" being replaced with 4 might not accurately represent the actual counts in some cases. The inaccuracies introduced by this approach could affect any subsequent analysis relying on the count variable.

c)  Calculate the total number of babies born in Munich in 2022
    and 2023. Which year had the bigger baby-boom?
    
```{r}
library(tidyverse)

vornamen_2022 %>% 
  summarise(total = sum(Anzahl))

vornamen_2023 %>% 
  summarise(total = sum(Anzahl))
```
The total number of babies born in Munich in 2022 is 9899, while in 2023 it is 24229. Therefore, 2023 had the bigger baby boom.

d)  Add a new column `year` to both datasets which holds the correct
    year for each.

```{r}
vornamen_2022 <- vornamen_2022 %>% 
  mutate(year = 2022)

vornamen_2023 <- vornamen_2023 %>% 
  mutate(year = 2023)
```

e)  Combine both datasets into one using `bind_rows()`.

```{r}
vornamen_combined <- bind_rows(vornamen_2022, vornamen_2023)
```


f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.

```{r}
vornamen_combined %>%
  group_by(Vorname) %>%
  summarise(total_count = sum(Anzahl)) %>% 
  arrange(desc(total_count)) %>% 
  slice_head(n = 10) %>% 
  knitr::kable(caption = "Top 10 names in Munich in 2022 and 2023")
```


## Exercise 4: Open Analysis (4 points)

This exercise is a bit more open-ended. You can choose any dataset from
[Our World in Data](https://ourworldindata.org/) and analyze it, while
determining the research question yourself.

a)  Go to <https://github.com/owid/owid-datasets/tree/master/datasets>
    and choose a dataset that interests you. You can have a look at
    <https://ourworldindata.org/> to gather some inspiration.
b)  Download the dataset and track it in git.
c)  Put the name / title of the dataset and a link to it below.

-   Dataset Name: Basic reading and maths skills - World Development Report (2018)
-   Link: <https://github.com/owid/owid-datasets/tree/master/datasets/Basic%20reading%20and%20maths%20skills%20-%20World%20Development%20Report%20(2018)>

d)  Come up with a (research) question you want to answer with the data
    and briefly explain why you believe this is an interesting question
    within one sentence. It should be a question that can be answered
    with the dataset and using R.

Which country listed in this dataset has the highest percentage of students who could not read a single word of a short text in 2015?

e)  Use R to answer your chosen question.

```{r}
rs <- read_csv("Basic reading and maths skills - World Development Report (2018).csv")

rs %>% 
  arrange(desc(`Percent of students who could not read a single word of a short text`)) %>% 
  slice(1) %>%
  select(Entity, `Percent of students who could not read a single word of a short text`)
```
Malawi has the highest percentage of students who could not read a single word of a short text in 2015


f)  Create a meaningful plot / figure with the dataset. Make sure to
    provide a figure caption (via the chunk options / Rmarkdown) and
    correctly label the figure.

```{r reading_skills, fig.cap = "Percent of students who could not read a single word of a short text in 2015", fig.align = 'left'}
ggplot(
  data = rs,
  mapping = aes(
    x = Entity,
    y = `Percent of students who could not read a single word of a short text`
  )
) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip()
```


## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
